Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
Finished first version of future work

\section*{Conclusion}
\section*{Future Work}
The results achieved over this dataset were significant. In order to show that
the techniques are general, though, we would like to run the same experiments on
other datasets, with different types of items and user behavior. Most of the 
assumptions made for this model were not specific to the data used, and so we 
hope to achieve similar results. It would also be interesting to see how 
different the learned parameters would be for other datasets and how well 
the techniques could perform using the same parameters learned here.

We would also like to investigate the use of latent variable

@@

\bibitem{Su2009}
    Xiaoyuan Su and Taghi M. Khoshgoftaar.
    ``A Survey of Collaborative Filtering Techniques.''
    \emph{Advances in Artificial Intelligence.} vol. 2009,
    Article ID 421425, 19 pages, 2009. doi:10.1155/2009/421425
\bibitem{Breese1998}
    John S. Breese, David Heckerman, and Carl Kadie, 
    ``Empirical analysis of predictive algorithms for collaborative filtering.'' 
    \emph{Proceedings of the Fourteenth conference on Uncertainty in artificial intelligence.}
    Morgan Kaufmann Publishers Inc., 1998.
\bibitem{Lemire1998}
    Daniel Lemire and Anna Maclachlan.
    ``Slope One Predictors for Online Rating-Based Collaborative Filtering.''
    \emph{SDM.} Vol. 5, 2005.
\bibitem{Koren2009}
    Yehuda Koren, Robert Bell, and Chris Volinsky. 
    ``Matrix factorization techniques for recommender systems.''
    \emph{Computer} 42.8, 2009. 30-37.

\end{thebibliography}

>>>>

\section*{Conclusion}
\section*{Future Work}
The results achieved over this dataset were significant. In order to show that
the techniques are general, though, we would like to run the same experiments on
other datasets, with different types of items and user behavior. The 
assumptions made for this model were not specific to the data used, so we 
hope to achieve similar results. It would also be interesting to see how 
different the learned parameters would be for other datasets and how well 
the techniques could perform using the same parameters learned here.

We would also like to incorporate latent factors into our model.
Latent factor techniques, such as the those presented in \cite{Koren2009}, have
become very popular since the Netflix Challenge and have proved to be better for
predicting user-item rating than classical CF. One experiment would be to
construct a new $TrueSimLatent$ based on the similarity of two items in 
latent factor space. Then we could apply both of the approaches in this
paper analagously in latent factor space. Another idea is to use latent factors 
as a new input to a model for predicting $TrueSimRand$ or $TrueSimPref$.

One difficulty with each of these experiments is that it is time consuming to 
compute the latent factors at different points in simulated time. Since we could
not recompute the matrix factorization for every new user rating, we would 
instead compute the latent factorization of the whole matrix at a few 
``snap-shots'' in simulated time. We then calculate the latent factors of many
different pairs at this time, each varying in their degrees of certainty. 
Hopefully, this should give enough pairs with dfferent degrees of certainty 
to train and test over.

In a different direction, we believe there are a number of possible applications
of the user predictivity score presented in this paper. Based on the results
found here, it is reasonable to believe that adding weights to users by their
predictivity would increase the performance of any user-item rating predictor.
The predictivity could also have applications in the problem of Robust
Collaborative Filtering \cite{Mehta2007}, where rating data is particularly noisy
or riddled with spam.

@@

\bibitem{Su2009}
    Xiaoyuan Su and Taghi M. Khoshgoftaar.
    ``A Survey of Collaborative Filtering Techniques.''
    \emph{Advances in Artificial Intelligence.} vol. 2009,
    Article ID 421425, 19 pages, 2009. doi:10.1155/2009/421425
\bibitem{Breese1998}
    John S. Breese, David Heckerman, and Carl Kadie, 
    ``Empirical analysis of predictive algorithms for collaborative filtering.'' 
    \emph{Proceedings of the Fourteenth conference on Uncertainty in artificial intelligence.}
    Morgan Kaufmann Publishers Inc., 1998.
\bibitem{Lemire1998}
    Daniel Lemire and Anna Maclachlan.
    ``Slope One Predictors for Online Rating-Based Collaborative Filtering.''
    \emph{SDM.} Vol. 5, 2005.
\bibitem{Koren2009}
    Yehuda Koren, Robert Bell, and Chris Volinsky. 
    ``Matrix factorization techniques for recommender systems.''
    \emph{Computer} 42.8, 2009. 30-37.
\bibitem{Mehta2007}
    Bhaskar Mehta, Thomas Hofmann, and Wolfgang Nejdl.
    ``Robust collaborative filtering.'' 
    \emph{Proceedings of the 2007 ACM conference on Recommender systems.}
    ACM, 2007.
\end{thebibliography}
